---
title: "Initial Korean covid 19"
author: "Marcia Sanchez"
date: "6/21/23"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
 
 
  
# Your Question - Is dying independent of sex?

## METHODS

We will analyze the Sex of the patients and the result if they are alive or dead. I will use the variables in my collection of Cat~Cat. This is a type of problem that we can use the helper file and we will copy into our project to get the correct answer. 








## Graphical results - use ggplot commands to do this 


#### Plot barplots ggplot way
```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

 In the counting chart I can see that not a lot people died. it is 50-70. In the percentage female is 50% is alive male is about 40. There is more female than male. Twice as many male are dying.  





  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
In the percentages I can see that more females are alive with the difference of 12%. Of all people that are dead 36% is female and 64% are male. in the second chart I see that females are 98.7 alive and males are only 97. In the dead % female were 1.4% and males at 3%. 

## Inferential results 




## Conclusions

